---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
```

\begin{center}
\huge{\underline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.25\textwidth}
\faLinkedin \centering\href{https://www.linkedin.com/in/darwin-del-castillo/}{\hspace{0.5em}darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.25\textwidth}
\faEnvelope \centering\href{mailto:ddelcastillo.f@gmail.com}{\hspace{0.5em}ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.20\textwidth}
\faGithub \centering\href{https://github.com/ddelcastillof}{\hspace{0.5em}ddelcastillof} 
\end{minipage}
\vspace{-2.5pt}
\end{center}

\section{Education}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Master of Public Health (MPH)} & \textbf{Sep 2023 – Jun 2025} \\
\textsc{University of Washington, USA} & \\
& \\
\textbf{Medical Doctor (MD)} & \textbf{Mar 2013 – Dec 2020} \\
\textsc{Universidad Nacional Mayor de San Marcos, Peru} & \\
\end{longtable}

\section{Additional Education}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textsc{Universidad Peruana Cayetano Heredia, Lima - Peru} & \\
\end{longtable}

\section{Professional Experience}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Graduate Research Assistant} & \textbf{Jul 2024 – Jun 2025} \\
\multicolumn{2}{p{18cm}}{\textsc{Institute for Health Metrics and Evaluation}} \\
\multicolumn{2}{p{18cm}}{\textsc{University of Washington, Seattle - USA}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Modeling epidemiological data of lower respiratory tract infections due to human metapneumovirus from 2010 to 2023 using meta-analysis information in R and Bayesian meta-regression suites (DisMod-MR).
  \item Analyzed data from public sources using Bayesian methods and Monte Carlo simulation to estimate the overlap proportion between socially excluded groups in high-income countries using the packages rJAGS and rstan.
  \item Estimated population-attributable fractions and standardized mortality ratios for socially excluded groups in high-income countries.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant} & \textbf{Jun 2024 – Mar 2025} \\
\multicolumn{2}{p{18cm}}{\textsc{Department of Global Health}} \\
\multicolumn{2}{p{18cm}}{\textsc{University of Washington, Seattle - USA}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Conducted a scoping review protocol and performed evidence synthesis for mapping potential indicators for implementing mental health policy in data-limited settings.
  \item Designed of a mixed-method study protocol to assess the effectiveness of implementation strategies for pediatric burn care in a Peruvian healthcare setting.
  \item Crafted communication strategies with stakeholders to inform results from the mixed-methods study.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant} & \textbf{Sep 2023 – Dec 2023} \\
\multicolumn{2}{p{18cm}}{\textsc{Department of Health Systems and Population Health}} \\
\multicolumn{2}{p{18cm}}{\textsc{University of Washington, Seattle - USA}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Gathered sociodemographic and utilization data as part of a clinical trial post-assesment survey through on-phone interviews.
  \item Translated IRB submissions materials from Spanish to English for the Alzheimer’s Disease Research Center.
  \item Synthesized early engagement and outreach data into visualisation tools and summary tables, enabling program managers to make adjustments to recruitment strategies.
\end{itemize}
} \\
\\
\textbf{Research Consultant} & \textbf{Jan 2023 – Jan 2024} \\
\multicolumn{2}{p{18cm}}{\textsc{Health Technology Assessment and Research Institute}} \\
\multicolumn{2}{p{18cm}}{\textsc{Social Security Health System, Lima - Peru}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Structured and consolidated multi-source health data (surveillance data, clinical studies) to generate data for health technology assessments.
  \item Conducted budget impact and cost-effectiveness assessments to prioritize funding for high-impact health interventions under national budgets.
  \item Presented data-driven recommendations and evidence summaries to policymakers and partners, supporting strategic purchasing decisions for the Social Security System.
\end{itemize}
} \\
\newpage
\textbf{Research Assistant} & \textbf{Mar 2019 – Aug 2023} \\
\multicolumn{2}{p{18cm}}{\textsc{CRONICAS Center of Excellence in Chronic Diseases}} \\
\multicolumn{2}{p{18cm}}{\textsc{Universidad Peruana Cayetano Heredia, Lima - Peru}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Coordinated focus groups and on-field work across four Peruvian regions to co-design an intervention for patients with cognitive impairment and their caregivers.
  \item Contributed to research grant proposals in hypertension, diabetes, cancer, and multimorbidity projects by conducting systematic reviews and preliminary data analysis.
  \item Co-authored scientific manuscripts in the topics mentioned above which included longitudinal data analyses, meta-analyses, and unsupervised machine learning methods.
\end{itemize}
} \\
\end{longtable}

\section{Skills}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{minipage}[c]{0.65\textwidth}
Health data science and epidemiology: data wrangling, querying, analysis, visualization \& management
\vspace{1pt}
\begin{itemize}
\item SQL (MySQL), Python, R programming
\item HPC (Slurm), Linux environments (bash)
\item VS Code, Jupyter Lab, Quarto, Markdown, \LaTeX, Shiny (R), GIS tools
\item Team-based projects on Github and Bitbucket repositories
\item Packages: tidyverse, ggplot2, meta/metafor, lme4, survival, geepack, gam, lavaan, sf, rJAGS, rstan, Pandas, Matplotlib, NumPy, MR-BRT (GBD Study estimation), amongst other tools.
\end{itemize}
\end{minipage}
\begin{minipage}[c]{0.35\textwidth}
\begin{itemize}
\item Fluency in English \& Spanish
\item Team work \& collaboration
\item Problem solving
\item Science communication
\item Mentorship
\end{itemize}
\end{minipage}

\section{Academic Honours and Awards}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{>{\raggedright\arraybackslash}p{16.5cm} p{1.5cm}} %%Improve the cum laude line%%
Young Lives Study Methodological Workshop Scholarship, \textsc{Group for the Analysis of Development (GRADE)} – Peru & \textbf{Jun 2018}\\
& \\
Medical School Graduation with Honors \textit{(Cum Laude)} (Grade: 17/20), \textsc{Universidad Nacional Mayor de San Marcos School of Medicine} – Peru & \textbf{Aug 2021}\\ 
& \\
Professional Certificate in Clinical Research Fogarty Scholarship, \textsc{Universidad Peruana Cayetano Heredia School of Public Healh} – Peru & \textbf{Sep 2021}\\
& \\
Department of Global Health Endowed Fellowship for Global Health Excellence, Equity and Impact, \textsc{University of Washington Department of Global Health} – USA & \textbf{Feb 2024}\\
\end{longtable}

\section{Research and Teaching}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\subsection{Research Support}
```{r importing grants, include = F, echo = F}
grants <- get_cv_sheet('grants') |>
  mutate(
    status  = ifelse(is.na(status), '', paste0(status)),
    role = ifelse(is.na(role), '', paste0(role)),
    project_code = ifelse(is.na(id), '', paste0(id)),
    budget   = ifelse(is.na(budget_total), '', paste0(budget_total)),
    awarded   = ifelse(is.na(awarded), '', paste0(awarded)),
    funder_1 = ifelse(is.na(sponsor_1), '', paste0(sponsor_1)),
    funder_2 = ifelse(is.na(sponsor_2), '', paste0(sponsor_2)),
    year_start = ifelse(is.na(begin), '', paste0(begin)),
    year_end = ifelse(is.na(end), '', paste0(end)),
    title = ifelse(is.na(title), '', paste0(enquote(title))),
    pi = ifelse(is.na(pi), '', paste0(pi, '.')),
    coi_1 = ifelse(is.na(coi_1), '', paste0(coi_1, '.')),
    coi_2 = ifelse(is.na(coi_2), '', paste0(coi_2, '.'))
    ) |> 
  arrange(desc(status))
```
\subsubsection{Concluded Research Support}
```{r grants_text}
#| results: asis
make_grants_table(grants, "concluded")
```
\newpage
\subsection{Teaching and Lecturer Contributions} <!-- Improve the pull method from the cv database -->
\begin{longtable}{>{\raggedright\arraybackslash}p{14cm} p{4cm}}
\textbf{Lecturer} & \textbf{Mar 2025 – Current} \\
\textsc{School of Medicine} & \\
\textsc{Universidad Científica del Sur, Lima – Peru} & \\
\textsc{Introduction to Epidemiology:} I teach three sections of \textasciitilde 15 fourth-year medical students each, focusing on basic clinical epidemiology concepts, including study designs, bias identification, \& basic epidemiological surveillance concepts. & \\
& \\
\textbf{Teaching Assistant} & \textbf{Mar 2024 – Jun 2024} \\
\textsc{College of Arts \& Sciences} & \\
\textsc{University of Washington, Seattle – USA} & \\ 
\textsc{Introduction to Molecular and Cellular Biology:} Led two laboratory practice sessions with \textasciitilde 25 undergraduate students each, covering fundamental molecular and cellular biology experiments. & \\
\end{longtable}

\subsection{Advising}
```{r}
#| name: pooling_advising_data
advisees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' – ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', '\\textsc{', institution, '}',', ',country,' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
```
\subsubsection{Undergraduate Students}
```{r}
#| results: asis
advisees |> 
  filter(complete == 0) |>
  make_bullet_list_filtered("ug")
```

\section{Publications \hspace{1cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

```{r gstext, include = F, echo = F, eval = T}
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\subsection{Google Scholar Statistics:} `r text_gs`

```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0(journal_abbv)),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) %>% 
  arrange(desc(pub_date))
```

\subsection{Peer-Reviewed Publications}
```{r printing papers}
#| results: asis
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference Abstracts}
```{r printing abstracts, eval = T, include = T, echo = F}
#| results: asis
make_bullet_list_filtered(pubs, "conference")
```

\subsection{Thesis and Dissertations}
```{r printing theses, eval = T, include = T, echo = F}
#| results: asis
make_bullet_list_filtered(pubs, "thesis")
```

\subsection{White Papers}
```{r printing white papers, eval = T, include = T, echo = F}
#| results: asis
make_bullet_list_filtered(pubs, "white_paper")
```

```{r future chunk of text, eval = F, include = F, echo = F}
\subsection{Databases}

\begin{longtable}{p{4cm} p{14cm}}
Pokemón GO Study & \href{https://figshare.com/articles/dataset/Personality_profiles_and_Pokemon_GO_engagement_csv/21191500?file=37569835}{Cross-sectional study: Exploratory factorial analysis database}
\end{longtable}
```

\section{Licensure and Certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{>{\raggedright\arraybackslash}p{17cm} p{1cm}}
Peruvian College of Physicians, Membership No. 94534 & \textbf{2021} \\
CITI Program, Good Clinical Practice and ICH, Credential ID 65079238 & \textbf{2023} \\
National Registry of Investigators \textsc{(RENACYT-CONCYTEC)}, Investigator Level VII (P0160977) & \textbf{2024} \\
\end{longtable}

```{r, eval = F, include = F, echo = F}
#| name: leadership
\section{Leadership, Volunteer, and Community Activities}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}

\textbf{Jan 2025 - current} & \textbf{Trainee Advisory Committee Member} \\
& \textbf{Consortium of Universities for Global Health, USA} \\
& Collaborating with international co-trainees to address global health challenges and provide student perspectives on global health issues such as COVID-19, racial disparities, climate change, and research involvement of global health students. \\

&\\

\textbf{Mar 2014 - current} & \textbf{Emeritus member and External advisor} \\
& \textbf{\href{https://cem.edu.pe/adiecs/}{Association for the Development of Student's Research in Health Sciences (ADIECS)}, Lima - Peru} \\
& Peruvian student association funded in 2008 by students from the Universidad Nacional Mayor de San Marcos to develop capacity of both hard (e.g., epidemiological study designs, data analysis) and soft skills (e.g., teamwork communication, problem-solving) for biomedical underserved students. \\

&\\

\textbf{Jan 2019 - Feb 2019} & \textbf{Medical volunteer} \\
& \textbf{Healing the Children Northeast, Ica - Peru} \\
& Medical translator during plastic surgery clinical rounds after surgery for cleft palate and cleft lip repairment in underserved populations. \\

&\\

\textbf{Nov 2019 - Dec 2019} & \textbf{Medical volunteer} \\
& \textbf{Healing the Children Rocky Mountains, Lima - Peru} \\
& Shadowed otorhinolaryngologist specialist before and after cochlear implant surgery in pediatric patients. Also helped as medical translator during clinical rounds. \\

\end{longtable}
```

\section{Memberships in Professional Organizations}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{itemize}
 \item International Epidemiological Association (2020 - Current)
 \item Peruvian College of Physicians (2021 - Current)
 \item Consortium of Universities for Global Health (2023 - Current)
 \item America’s Network for Chronic Disease Surveillance (2025 - Current)
\end{itemize}