---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
```

\begin{center}
\huge{\underline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.25\textwidth}
\faLinkedin \centering\href{https://www.linkedin.com/in/darwin-del-castillo/}{\hspace{0.5em}darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.25\textwidth}
\faEnvelope \centering\href{mailto:ddelcastillo.f@gmail.com}{\hspace{0.5em}ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.20\textwidth}
\faGithub \centering\href{https://github.com/ddelcastillof}{\hspace{0.5em}ddelcastillof} 
\end{minipage}
\vspace{-2.5pt}
\end{center}

\section{Education}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}
\textbf{Sep 2023 – May 2025} & \textbf{Master in Public Health (MPH)} \\
&\textbf{University of Washington, USA} \\
&\\
\textbf{Mar 2013 – Dec 2020} & \textbf{Medical Doctor (MD)} \\
&\textbf{Universidad Nacional Mayor de San Marcos, Peru} \\
\end{longtable}

\section{Additional Education}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}
\textbf{Sep 2021 – Apr 2022} & \textbf{Professional Certificate in Clinical Research} \\
& \textbf{Universidad Peruana Cayetano Heredia, Lima - Peru} \\
\end{longtable}

\section{Professional Experience}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}
\textbf{Jul 2024 – Jun 2025} & \textbf{Graduate Research Assistant} \\
& \textbf{Institute for Health Metrics and Evaluation} \\
& \textbf{University of Washington, Seattle - USA} \\
& \begin{itemize}
\item Modeling epidemiological data of lower respiratory tract infections due to human metapneumovirus from 2010 to 2023 using meta-analysis information in R and Bayesian meta-regression suites (DisMod-MR).
\item Analyzed data from public sources using Bayesian methods and Monte Carlo simulation to estimate the overlap proportion between socially excluded groups in high-income countries using the packages rJAGS and rstan.
\item Improved analytic scripts for electronic health records data extraction, cleaning, and analysis by developing Python functions and pipeline tools that reduced processing time.
\end{itemize} \\
\\
\textbf{Jun 2024 – Mar 2025} & \textbf{Graduate Research Assistant} \\
& \textbf{Department of Global Health} \\
& \textbf{University of Washington, Seattle - USA} \\
& \begin{itemize}
\item Conducted a scoping review protocol and performed evidence synthesis for mapping potential indicators for implementing mental health policy in data-limited settings.
\item Designed of a mixed-method study protocol to assess the effectiveness of implementation strategies for pediatric burn care in a Peruvian healthcare setting.
\item Crafted communication strategies with stakeholders to inform results from the mixed-methods study.
\end{itemize} \\
\\
\textbf{Sep 2023 – Dec 2023} & \textbf{Graduate Research Assistant} \\
& \textbf{Department of Health Systems and Population Health} \\
& \textbf{University of Washington, Seattle - USA} \\
& \begin{itemize}
\item Gathered sociodemographic and utlization data as part of a clinical trial post-assesment survey through on-phone interviews.
\item Translated IRB submissions materials from Spanish to English for the Alzheimer’s Disease Research Center.
\item Synthesized early engagement and outreach data into visualisation tools and summary tables, enabling program managers to make adjustments to recruitment strategies.
\end{itemize} \\
\newpage
\textbf{Jan 2023 – Jan 2024} & \textbf{Research Consultant} \\
& \textbf{Health Technology Assessment and Research Institute} \\
& \textbf{Social Security Health System, Lima - Peru} \\
& \begin{itemize}
\item Structured and consolidated multi-source health data (surveillance data, clinical studies) to generate data for health technology assessments.
\item Conducted budget impact and cost-effectiveness assessments to prioritize funding for high-impact health interventions under national budgets.
\item Presented data-driven recommendations and evidence summaries to policymakers and partners, supporting strategic purchasing decisions for the Social Security System.
\end{itemize} \\
\\
\textbf{Mar 2019 – Aug 2023} & \textbf{Research Assistant} \\
& \textbf{CRONICAS Center of Excellence in Chronic Diseases} \\
& \textbf{Universidad Peruana Cayetano Heredia, Lima - Peru} \\
& \begin{itemize}
\item Coordinated focus groups and on-field work across four Peruvian regions to co-design an intervention for patients with cognitive impairment and their caregivers.
\item Contributed to research grant proposals in hypertension, diabetes, cancer, and multimorbidity projects by conducting systematic reviews and preliminary data analysis.
\item Co-authored scientific manuscripts in the topics mentioned above which included longitudinal data analyses, meta-analyses, and unsupervised machine learning methods.
\end{itemize} \\
\end{longtable}

\section{Skills}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{minipage}[c]{0.65\textwidth}
Health data science and epidemiology: data wrangling, querying, analysis, visualization \& management
\vspace{1pt}
\begin{itemize}
\item SQL (MySQL), Python, R programming
\item HPC (Slurm), Linux environments (bash)
\item VS Code, Jupyter Lab, Quarto, Markdown, \LaTeX, Shiny (R), GIS tools
\item Team-based projects on Github and Bitbucket repositories
\item Packages: tidyverse, ggplot2, meta/metafor, lme4, survival, geepack, gam, lavaan, sf, rJAGS, rstan, Pandas, Matplotlib, NumPy, MR-BRT (GBD Study estimation), amongst other tools.
\end{itemize}
\end{minipage}
\begin{minipage}[c]{0.35\textwidth}
\begin{itemize}
\item Fluency in English \& Spanish
\item Team work \& collaboration
\item Problem solving
\item Science communication
\item Mentorship
\end{itemize}
\end{minipage}

\section{Academic Honours and Awards}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{>{\raggedright\arraybackslash}p{1.5cm} p{16.5cm}}
\textbf{Jun 2018} & Scholarship for the Young Lives Study’s Methodological Workshop, GRADE Research Group. A workshop to receive advanced training in data wrangling and longitudinal data analysis applied to the Young Lives Study. \\
& \\
\textbf{Jul 2021} & Graduated with Honours \textit{(Cum Laude)}, School of Medicine, Universidad Nacional Mayor de San Marcos. Grade of 17/20 \\
& \\
\textbf{Sep 2021} & Scholarship to study the Diplomate in Clinical Research at Universidad Peruana Cayetano Heredia. Funded by the training program NIH/FIC 2D43TW001140-21 “Training in Infectious Disease in Peru – Time for Implementation Research,” Universidad Peruana Cayetano Heredia \\
& \\
\textbf{Feb 2024} & Department of Global Health Endowed Fellowship for Global Health Excellence, Equity and Impact, University of Washington \\
\end{longtable}

```{r past skills text, eval = F, include = F, echo = F}
### Qualitative analysis skills: Intermediate skills in qualitative data analysis, 
### thematic coding, content analysis, and experience with the software Dedoose.

\section{\underline{Skills}}

\begin{justify}
\textbf{Computer and programming skills:} 
\begin{itemize}
\item \textbf{Programming languages:} R, Python, bash
\item \textbf{Statistical software:} Stata, SPSS, SAS, G*Power
\item \textbf{Data visualization and reporting:} Shiny, ArcGIS, \LaTeX, Markdown
\item \textbf{Data management and wrangling:} SQL, REDCap
\item \textbf{Project management:} Jira, Asana, Trello
\item \textbf{Development tools:} Git, GitHub, Docker, VSCode, Confluence, Bitbucket 
\item \textbf{Computing environments:} Linux/Unix, Windows, ssh
\end{itemize}

\textbf{Languages:} 
\begin{longtable}{>{\centering\arraybackslash}p{6cm}>{\centering\arraybackslash}p{6cm}>{\centering\arraybackslash}p{6cm}}
English: Fluent & Spanish: Native & Portuguese: Working proficiency
\end{longtable}
\end{justify}
```

\section{Publications \hspace{1cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

```{r gstext, include = F, echo = F, eval = T}
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\subsection{Google Scholar Statistics:} `r text_gs`

```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0(journal_abbv)),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) %>% 
  arrange(desc(pub_date))
```

\subsection{Peer-Reviewed Publications}
```{r printing papers}
#| results: asis
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference Abstracts}
```{r printing abstracts, eval = T, include = T, echo = F}
#| results: asis
make_bullet_list_filtered(pubs, "conference")
```

\subsection{Thesis and Dissertations}
```{r printing theses, eval = T, include = T, echo = F}
#| results: asis
make_bullet_list_filtered(pubs, "thesis")
```

\subsection{White Papers}
```{r printing white papers, eval = T, include = T, echo = F}
#| results: asis
make_bullet_list_filtered(pubs, "white_paper")
```

```{r future chunk of text, eval = F, include = F, echo = F}
\subsection{Databases}

\begin{longtable}{p{4cm} p{14cm}}
Pokemón GO Study & \href{https://figshare.com/articles/dataset/Personality_profiles_and_Pokemon_GO_engagement_csv/21191500?file=37569835}{Cross-sectional study: Exploratory factorial analysis database}
\end{longtable}
```

```{r classes at UNMSM, eval = F, include = F, echo = F}
df <- get_cv_sheet('classes') |> filter(univ == "UNMSM") |>
    mutate(
      course = paste0(name),
      role = type,
      semester = ifelse(semester == 'Aut20', 'Aut20', semester)
    ) |> 
    select(
      Semester = semester,
      Course = course,
      Role = role,
      Level = level
    ) 

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "")
```

```{r classes at ucsur, eval = F, include = F, echo = F}
df <- get_cv_sheet('classes') |> filter(univ == "UCSUR") |>
    mutate(
      course = paste0(name),
      role = type,
      semester = ifelse(semester == '
                        Sum25', 'Sum25', semester)
    ) |> 
    select(
      Semester = semester,
      Course = course,
      Role = role,
      Level = level
    ) 

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "")
```

```{r classes uw, eval = F, include = F, echo = F}
df <- get_cv_sheet('classes') |> filter(univ == "UW") |>
    mutate(
      course = paste0(name),
      role = type, 
      semester = ifelse(semester == 'Spr24', 'Spr24', semester)
      ) |> 
    select(
      Semester = semester,
      Course = course,
      Role = role,
      Level = level
    ) 

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "")
```

```{r other teaching, eval = F, include = F, echo = F}
teaching <- get_cv_sheet('teaching') |>
  arrange(desc(date)) |> 
  mutate(
    with = ifelse(is.na(with), '', paste0(', with ', with)),
    title = paste0(enquote(title), with),
    date = paste0(format(as.Date(date), format = "%b %d, %Y"), '.'),
    url = ifelse(is.na(url), NA, markdown_url(url)),
    date = ifelse(is.na(url), date, paste0(date, '. ', url)), 
    citation = paste(title, host, location, date, sep = '. ')
  )
```

```{r seminars, eval = F, include = F, echo = F}
#| results: asis
make_ordered_list_filtered(teaching, "seminar")
```

\section{Advising}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

```{r}
#| name: pooling_advising_data
advisees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' to ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', institution, ' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
```
\subsection{Undergraduate Students - Current}
```{r}
#| results: asis
advisees |> 
  filter(complete == 0) |>
  make_ordered_list_filtered("ug")
```

\section{Licensure and certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{>{\raggedright\arraybackslash}p{1cm} p{17cm}}
\textbf{2021} & Peruvian College of Physicians, Membership No. 94534 \\
\textbf{2024} & National Registry of Investigators, RENACYT-CONCYTEC, Investigator Level VII (P0160977) \\
\end{longtable}

```{r, eval = F, include = F, echo = F}
#| name: leadership
\section{Leadership, Volunteer, and Community Activities}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}

\textbf{Jan 2025 - current} & \textbf{Trainee Advisory Committee Member} \\
& \textbf{Consortium of Universities for Global Health, USA} \\
& Collaborating with international co-trainees to address global health challenges and provide student perspectives on global health issues such as COVID-19, racial disparities, climate change, and research involvement of global health students. \\

&\\

\textbf{Mar 2014 - current} & \textbf{Emeritus member and External advisor} \\
& \textbf{\href{https://cem.edu.pe/adiecs/}{Association for the Development of Student's Research in Health Sciences (ADIECS)}, Lima - Peru} \\
& Peruvian student association funded in 2008 by students from the Universidad Nacional Mayor de San Marcos to develop capacity of both hard (e.g., epidemiological study designs, data analysis) and soft skills (e.g., teamwork communication, problem-solving) for biomedical underserved students. \\

&\\

\textbf{Jan 2019 - Feb 2019} & \textbf{Medical volunteer} \\
& \textbf{Healing the Children Northeast, Ica - Peru} \\
& Medical translator during plastic surgery clinical rounds after surgery for cleft palate and cleft lip repairment in underserved populations. \\

&\\

\textbf{Nov 2019 - Dec 2019} & \textbf{Medical volunteer} \\
& \textbf{Healing the Children Rocky Mountains, Lima - Peru} \\
& Shadowed otorhinolaryngologist specialist before and after cochlear implant surgery in pediatric patients. Also helped as medical translator during clinical rounds. \\

\end{longtable}
```

\section{Other activities}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{>{\raggedright\arraybackslash}p{3.5cm} p{14.5cm}}
\textbf{Jan 2025 – current} & \textbf{Lecturer: Introduction to Epidemiology.} Universidad Científica del Sur. I'm teaching fourth-year medical students basic concepts of clinical epidemiology with a focus on basic study designs and identification of bias.
\end{longtable}

\section{Memberships in Professional Organizations}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{itemize}
 \item International Epidemiological Association (2020 - Current)
 \item Peruvian College of Physicians (2021 - Current)
 \item Consortium of Universities for Global Health (2023 - Current)
 \item America’s Network for Chronic Disease Surveillance (2025 - Current)
\end{itemize}