---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
```

\par\centering{\Large{Darwin Del Castillo Fernandez, M.D.}}
\vspace{-5pt}
\par\centering{Department of Global Health, University of Washington}
\vspace{-5pt}
\par\centering{Hans Rosling Center for Population Health}
\vspace{-5pt}
\par\centering{3980 15th Ave NE, Seattle, WA 98105}
\vspace{-5pt}
\par\centering{+1 (206) 605-5077 (USA) | +51 965-006-311 (Peru)}
\vspace{-5pt}
\par\centering{ddelcast@uw.edu}
\vspace{-5pt}
\par\centering{\href{https://ddelcastillof.github.io/darwindelcastillo/}{https://www.darwindelcastillo.com}}
\rule{\textwidth}{0.5pt}
\vspace{-10pt}

# Education

\begin{longtable}{p{4cm}p{12cm}}

\textbf{Graduate} & University of Washington, Seattle, US \\
& \textbf{Master in Public Health (M.P.H.), Global Health} \\
& \textbf{Sep 2023 – June 2025} \\
& \textit{Thesis:} “Cost-effectiveness analysis of a household salt substitute intervention on reducing community-wide blood pressure in Northern Peru” \\

& \\

\textbf{Undergraduate} & Universidad Nacional Mayor de San Marcos, Lima, Peru \\
& \textbf{Medical Doctor (M.D.), Medicine} \\
& \textbf{Mar 2013 – Aug 2021} \\
& \textit{Thesis:} "Childhood Obesity and Its Effect on Academic Achievement: An Analysis of the Young Lives Study between 2009 and 2016" \\

\end{longtable}

## Additional education

\begin{longtable}{p{4cm}p{12cm}}
\textbf{Graduate} & University of Washington, Seattle, US \\
& \textbf{Certificate in Global Health on Maternal and Child Health} \\
& \textbf{Nov 2023 – June 2025} \\

& \\

& Universidad Peruana Cayetano Heredia, Lima, Peru \\
& \textbf{Certificate in Clinical Research} \\
& \textbf{Sep 2021 – Apr 2022} \\

\end{longtable}

# Licensure and certification

\begin{longtable}{p{2cm}p{10cm}}

\textbf{2021} & Peruvian College of Physicians, Membership No. 94534 \\
\textbf{2024} & National Registry of Investigators, RENACYT-CONCYTEC, Investigator Level VII (P0160977) \\

\end{longtable}

# Professional Experience

\begin{longtable}{p{4cm}p{12cm}}

\textbf{Nov 2024 - Present} & Research Assistant \\
& Department of Global Health \\
& University of Washington, USA \\
& \begin{itemize}
\item Designing a systematic review protocol for mapping potential indicators for the implementation of mental health policy in data-limited resources
\item Coordinating a expert group panel for developing a set list of indicators based in structured expert elicitation
\item Engaging with stakeholders for the implementation of the future list of proposed indicators in a later phase of the project
\end{itemize} \\

& \\
& \\
& \\

\textbf{Aug 2024 - current} & Research Intern \\
& Cinical Informatics Team, Institute for Health Metrics and Evaluation \\
& University of Washington, USA \\
& \begin{itemize}
\item Estimated population attributable fractions and standardized mortality ratios for social excluded groups, i.e. people experiencing imprisonment, homelessness, and substance use disorders, in high-income countries.
\item Analyzed data from public sources and a previous systematic review using Bayesian methods and Monte Carlo simulation to estimate the overlap proportion between social excluded groups in high-income countries.
\item Collaborated in writing a R01 NIH research proposal to estimate the disease burden for social excluded groups in high-income countries.
\end{itemize} \\

& \\

\textbf{Jul 2024 - Sep 2024} & Research Assistant \\
& Department of Global Health \\
& University of Washington, USA \\
& \begin{itemize}
\item Led the design of a mixed-method study to assess the effectiveness of implementation strategies for pediatric burn care in a Peruvian healthcare setting
\item Collaborated with multidisciplinary teams at Seattle Children’s Hospital and the Peruvian National Hospital for Children to align study objectives and methodologies
\item Coordinated cross-cultural research efforts to ensure the study’s relevance and applicability to both U.S. and Peruvian healthcare environments 
\end{itemize} \\

& \\

\textbf{Sep 2023 - Dec 2023} & Research Assistant \\
& Department of Health Systems and Population Health \\
& University of Washington, USA \\
& \begin{itemize}
\item Conducted on-phone interviews for the second post-survey assessment of the ReOpening Schools Safely and Educating Youth Study (ROSSEY Study)
\item Supported submission of materials in Spanish for the IRB for the ADRC Clinical Core Study project
\item Conducted preliminary analyses for the Outreach, Engagement, and Recruitment module of the ADRC Clinical Core Study project
\end{itemize} \\

& \\

\textbf{Jun 2023 - Aug 2023} & Research Assistant \\
& CRONICAS Center of Excellence in Chronic Diseases \\
& Universidad Peruana Cayetano Heredia, Peru \\
& \begin{itemize}
\item Conducted semi-structured qualitative interviews for the NIHR-UK-supported IMPACT-DEMENTIA project, collaborating with researchers from Universidad Peruana Cayetano Heredia, Imperial College, and the University of Oxford
\item Facilitated collaboration and communication between international research teams and local stakeholders to ensure effective project implementation
\item Coordinated fieldwork with community health workers across diverse Lima, Iquitos, and Huancayo locations
\end{itemize} \\

& \\
& \\
& \\
& \\
& \\
& \\
& \\
& \\
& \\

\textbf{Jan 2023 - Jan 2024} & Research Consultant \\
& Health Technology Assessment and Research Unit \\
& Social Security Health System, Peru \\
& \begin{itemize}
\item Assessed the benefits and drawbacks of purchasing pharmaceutical products for Peru's social health insurance through a systematic evaluation of the effectiveness and economic impact
\item Conducted systematic reviews of anti-cancerous and immunosuppressant drugs regarding efficacy and economic impact
\item Evaluated the budget impact of introducing new pharmacological products in the Social Security System
\end{itemize} \\

& \\

\textbf{Mar 2022 - Mar 2023} & Clinical Sub-investigator \\
& Clinical Research Unit \\
& Via Libre Association, Peru \\
& \begin{itemize}
\item Via Libre is a Clinical Research Site for studies in STI and HIV prevention and treatment in queer population
\item Performed clinical procedures and assessed clinical trial participants from the HVTN and the HPTN networks
\item Participated and organized didactical activities in community outreach and participant retention crafted for the queer community
\end{itemize} \\

& \\

\textbf{Jun 2021 - Aug 2021} & Research Consultant \\
& Health Technology Assessment and Research Unit \\
& Social Security Health System, Peru \\
& \begin{itemize}
\item Managed and validated all data inputs using REDCap from two clinical studies related to COVID-19 vaccinations 
\item Contributed to a randomized controlled trial assessing the efficacy and safety of convalescent plasma therapy in COVID-19-infected patients
\item Conducted data analysis from an observational study on vaccination hesitancy among healthcare workers using Stata and R statistical packages
\end{itemize} \\

& \\

\textbf{Mar 2019 - Jun 2021} & Research Assistant \\
& CRONICAS Center of Excellence in Chronic Diseases \\
& Universidad Peruana Cayetano Heredia, Peru \\
& \begin{itemize}
\item Conducted a systematic review with the COSMOS initiative to develop a core set of outcomes for designing multimorbidity clinical trials.
\item Participated in the data handling and the writing phase of a research manuscript to understand the impact of preterm birth on the development of hypertension in offspring at age 22.
\item Collaborated in the study design and manuscript preparation of other research interim products, including peer-reviewed research articles
\end{itemize} \\

\end{longtable}

# Academic Honours and Awards
\begin{longtable}{p{2cm} p{12cm}}
\textbf{2018} & \begin{itemize} 
\item Scholarship for the Young Lives Study’s Methodological Workshop, GRADE Research Group. A workshop to receive advanced training in data wrangling and longitudinal data analysis applied to the Young Lives Study.
\end{itemize} \\
\textbf{2021} & \begin{itemize} 
\item Graduated with Honours \textit{(Cum Laude)}, School of Medicine, Universidad Nacional Mayor de San Marcos. Grade of 17/20
\item   Scholarship to study the Diplomate in Clinical Research at Universidad Peruana
Cayetano Heredia. Funded by the training program NIH/FIC 2D43TW001140-21 “Training in Infectious Disease in Peru – Time for Implementation Research,” Universidad Peruana Cayetano Heredia
\end{itemize} \\
\textbf{2024} & \begin{itemize} 
\item Department of Global Health Endowed Fellowship for Global Health Excellence, Equity and Impact, University of Washington
\end{itemize} \\
\end{longtable}

# Skills
\begin{justify}
\textbf{Computer and programming skills:} Advanced skills in R, Stata, and SPSS for statistical analysis, data visualization, decision-making analyses, and genetic epidemiology. Intermediate skills in Python for genomic data science, epidemiologic data analysis, and data wrangling. Certificates in data management, causal inference, and machine learning applied to healthcare. \\
Intermediate skills in qualitative data analysis, thematic coding, content analysis, and experience with the software Dedoose. \\
Competencies in Microsoft Office Suite (Word, PowerPoint, Excel), G*Power, and REDCap.\\
\textbf{Languages:} Spanish (native), English (fluent), French (basic)
\end{justify}

# Publications
```{r gstext, include = F, echo = F}
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\begin{longtable}{p{6cm} p{6cm}}
\href{`r gscholar_page`}{Google Scholar Profile} & ORCID: \href{https://orcid.org/0000-0002-8609-0312}{0000-0002-8609-0312} \\
\end{longtable}

\begin{justify}
Google Scholar Stats: `r text_gs`
\end{justify}

## Databases

\begin{longtable}{p{3cm} p{12cm}}
Pokemón GO Study & \href{https://figshare.com/articles/dataset/Personality_profiles_and_Pokemon_GO_engagement_csv/21191500?file=37569835}{Cross-sectional study: Exploratory factorial analysis database}
\end{longtable}

```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0(journal_abbv)),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi)
  ) %>% 
  arrange(desc(pub_date))
```

## Submitted Articles
```{r incoming}
#| results: asis
make_ordered_list_filtered(pubs, "other")
```

## Peer-Reviewed Publications
```{r printing references in pandoc format}
#| results: asis
make_ordered_list_filtered(pubs, "peer_reviewed")
```

## Pre-prints
```{r printing pre-print}
#| results: asis
make_ordered_list_filtered(pubs, "working")
```

## Policy Statements, White Papers, Reports
```{r printing white papers}
#| results: asis
make_ordered_list_filtered(pubs, "white_paper")
```

## Theses
```{r theses}
#| results: asis
make_ordered_list_filtered(pubs, "theses")
```

# Teaching Experience
## Courses taught at the college level
### Courses taught at Universidad Nacional Mayor de San Marcos
```{r}
df <- get_cv_sheet('classes') |> filter(univ == "UNMSM") |>
    mutate(
      course = paste0(number, ": ", name),
      role = type,
      num = paste(responses, '/', enrolled), 
      score = paste(inst_mean, '/', dept_mean), 
      semester = ifelse(semester == 'Aut20', 'Aut20$^†$', semester)
    ) |> 
    select(
      `Sem.` = semester,
      Course = course,
      Role = role,
      Level = level, 
      `N. Resp. / N. Enrolled` = num,
      `Instr. CE* / Dept Mean` = score
    ) 

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "") |> 
  column_spec(5, width = "1.8cm") |> 
  column_spec(6, width = "2cm") |> 
  footnote(
    symbol = c(
      "Course Evaluations (FCE) were scored by students (0 = worst, 20 = best).", 
      "No course evaluations were recorded in 2020 due to the COVID-19 pandemic."
    )
  )
```

### Courses taught at University of Washington
```{r}
df <- get_cv_sheet('classes') |> filter(univ == "UW") |>
    mutate(
      course = paste0(number, ": ", name),
      role = type,
      num = paste(responses, '/', enrolled), 
      score = paste(inst_mean, '/', dept_mean), 
      semester = ifelse(semester == 'Spr24', 'Spr24$^*$', semester)
      ) |> 
    select(
      `Sem.` = semester,
      Course = course,
      Role = role,
      Level = level, 
      `N. Resp. / N. Enrolled` = num,
      `Instr. CE / Dept Mean` = score
    ) 

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "") |> 
  column_spec(5, width = "1.8cm") |> 
  column_spec(6, width = "2cm") |>
  footnote(
    symbol = c("Couldn't send course evaluations due to health issues")
  )
```

## Other teaching experience
```{r}
teaching <- get_cv_sheet('teaching') |>
  arrange(desc(date)) |> 
  mutate(
    with = ifelse(is.na(with), '', paste0(', with ', with)),
    title = paste0(enquote(title), with),
    date = paste0(format(as.Date(date), format = "%b %d, %Y"), '.'),
    url = ifelse(is.na(url), NA, markdown_url(url)),
    date = ifelse(is.na(url), date, paste0(date, '. ', url)), 
    citation = paste(title, host, location, date, sep = '. ')
  )
```
### Seminars
```{r}
#| results: asis
make_ordered_list_filtered(teaching, "seminar")
```

# Advising
```{r}
advisees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' to ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', institution, ' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
```
## Undergraduate Students - Current
```{r}
#| results: asis
advisees |> 
  filter(complete == 0) |>
  make_ordered_list_filtered("ug")
```


# Leadership, Volunteer, and Community Activities
\begin{itemize}
  \item Emeritus member and External advisor, \href{https://cem.edu.pe/adiecs/}{Association for the Development of Student's Research in Health Sciences (ADIECS)}, Peru: Peruvian student association funded in 2008 by students from the Universidad Nacional Mayor de San Marcos with the aim of developing capacity of both hard (e.g., epidemiological study designs, data analysis) and soft skills (e.g., teamwork communication, problem-solving) for biomedical underserved students (Mar 2014-current).
  \item Medical volunteer, Healing the Children Northeast, Peru: Medical translator during plastic surgery clinical rounds after surgery for cleft palate and cleft lip repairment in undeserved populations (Jan 2019).
  \item Medical volunteer, Healing the Children Rocky Mountains, Peru: Shadowed ENT attendings before and after cochlear implant surgery in pediatric patients. Also helped as medical translator during clinical rounds (Nov 2019).
\end{itemize}

# Memberships in Professional Organizations
\begin{itemize}
 \item International Epidemiological Association (2020 — Current)
 \item Peruvian College of Physicians (2021 — Current)
\end{itemize}