---
format:
  pdf:
    output-file: cv.pdf
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "zC1dAvcAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
```

\begin{center}
\huge{\underline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.25\textwidth}
\faLinkedin \centering\href{https://www.linkedin.com/in/darwin-del-castillo/}{\hspace{0.5em}darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.25\textwidth}
\faEnvelope \centering\href{mailto:ddelcastillo.f@gmail.com}{\hspace{0.5em}ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.20\textwidth}
\faGithub \centering\href{https://github.com/ddelcastillof}{\hspace{0.5em}ddelcastillof} 
\end{minipage}
\vspace{-2.5pt}
\end{center}

\section{Education}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Master of Public Health (MPH)} & \textbf{Sep 2023 – Jun 2025} \\
\textsc{University of Washington} & \textsc{Seattle – USA}\\
& \\
\textbf{Doctor of Medicine (MD)} & \textbf{Mar 2014 – Aug 2021} \\
\textsc{Universidad Nacional Mayor de San Marcos} & \textsc{Lima – Peru}\\
\end{longtable}

\section{Additional Education}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textsc{Universidad Peruana Cayetano Heredia} & \textsc{Lima – Peru} \\
\end{longtable}

\section{Professional Experience}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Graduate Research Assistant} & \textbf{Jul 2024 – Jun 2025} \\
\textsc{Institute for Health Metrics and Evaluation} & \textsc{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Developed hyperparameters for a Bayesian hierarchical meta‑regression model to estimate prevalence, incidence, and clinical‐outcome occurrence of lower respiratory tract infections across 80 countries.
  \item Executed an MCMC using data-driven priors and uncertainty propagation to estimate the probabilistic overlap between inclusion health groups in 22 high-income countries.
  \item Estimated population-attributable fractions and standardized mortality ratios using the overlap between inclusion health groups.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant} & \textbf{Jun 2024 – Mar 2025} \\
\textsc{Department of Global Health – University of Washington} & \textsc{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Designed a study protocol to assess the effectiveness of implementation strategies for pediatric burn care in a Peruvian healthcare setting.
  \item Coordinated a mixed-methods study to explore barriers and facilitators in >10 low-resource Peruvian hospitals.
  \item Co-developed communication strategies with 2 stakeholder organizations to disseminate complex findings among healthcare policymakers.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant}  & \textbf{Sep 2023 – Mar 2024} \\
\textsc{Health Population Research Center – University of Washington} & \textsc{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Maintained and stored sociodemographic and utilization data as part of a clinical trial post-assessment survey on school-age children using electronic data capture platforms.
  \item Translated IRB submission materials from Spanish to English for the Alzheimer’s Disease Research Center.
  \item Analyzed engagement and outreach data from clinical trials into visualization tools and summary tables, enabling program managers to make adjustments to recruitment strategies.
\end{itemize}
} \\
\\
\textbf{Research Consultant} & \textbf{Jan 2023 – Jan 2024} \\
\textsc{Health Technology Assessment and Research Institute} & \textsc{Lima – Peru}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Integrated surveillance and clinical data from Peruvian hospitals into statistical burden models to support national health technology assessment and prioritization processes.
  \item Conducted budget impact and cost-effectiveness models that prioritized oncological interventions worth over \$1 M+.
  \item Synthesized findings into executive reports aimed at policymakers and partners, guiding reimbursement policy for Peru's Social Security System.
\end{itemize}
} \\
\newpage
\textbf{Research Assistant} & \textbf{Mar 2019 – Aug 2023}\\
\textsc{CRONICAS Center of Excellence in Chronic Diseases} & \textsc{Lima – Peru}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Coordinated 2 workshops per site with community health workers in 3 Peruvian regions to co-design a mobile application for early detection of cognitive impairment.
  \item Contributed to research grant proposals in noncommunicable disease epidemiology for pediatric and adult populations by conducting preliminary data analysis of clinical and demographic data, supporting research proposals.
  \item Co-authored 5 scientific manuscripts, including longitudinal data analyses, systematic reviews, and machine learning models.
\end{itemize}
} \\
\end{longtable}

\section{Skills}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
Broad experience in the health data lifecycle: data collection, management, wrangling, querying, analysis, \& visualization.
\vspace{1pt}
\textbf{Programming languages:} R, Python, C++, Stata, SQL (MySQL) \
\textbf{Cloud Computing:} Slurm HPC, Containerization (Docker/Apptainer), Linux environments (bash) \
\textbf{Tools:} VS Code, Jupyter, Quarto, \LaTeX, Shiny (R), Git version control (GitHub, Bitbucket) \
\textbf{Packages:} \texttt{tidyverse}, \texttt{ggplot2}, \texttt{sf}, \texttt{survey}, \texttt{lme4}, \texttt{survival}, \texttt{cmprsk}, \texttt{mice}, \texttt{geepack}, \texttt{metafor}, \texttt{rstan}, \texttt{crosswalk}, \texttt{pandas}, \texttt{NumPy}, \texttt{Matplotlib}, \texttt{pytest}, MR-BRT \
\textbf{Languages:} English (fluent), Spanish (native) \
\textbf{Core Competencies:} Data analysis, teamwork, problem solving, science communication, mentorship


\section{Academic Honours and Awards}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{>{\raggedright\arraybackslash}p{16.5cm} p{1.5cm}} %%Improve the cum laude line%%
Young Lives Study Methodological Workshop Scholarship, \textsc{Group for the Analysis of Development (GRADE)} – Peru & \textbf{Jun 2018}\\
& \\
Medical School Graduation with Honors \textit{(Cum Laude)} (Grade: 17/20), \textsc{Universidad Nacional Mayor de San Marcos School of Medicine} – Peru & \textbf{Aug 2021}\\ 
& \\
Professional Certificate in Clinical Research Fogarty Scholarship, \textsc{Universidad Peruana Cayetano Heredia School of Public Health} – Peru & \textbf{Sep 2021}\\
& \\
Department of Global Health Endowed Fellowship for Global Health Excellence, Equity and Impact, \textsc{University of Washington Department of Global Health} – USA & \textbf{Feb 2024}\\
\end{longtable}

\section{Research and Teaching}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\subsection{Research Support}
```{r importing grants, include = F, echo = F}
grants <- get_cv_sheet('grants') |>
  mutate(
    status  = na_to_space(status),
    role = na_to_space(role),
    project_code = na_to_space(id),
    budget   = na_to_space(budget_total),
    awarded   = na_to_space(awarded),
    funder_1 = na_to_space(sponsor_1),
    funder_2 = na_to_space(sponsor_2),
    year_start = na_to_space(begin),
    year_end = na_to_space(end),
    title = na_to_space(title),
    pi = ifelse(is.na(pi), '', paste0(pi, '.')),
    coi_1 = ifelse(is.na(coi_1), '', paste0(coi_1, '.')),
    coi_2 = ifelse(is.na(coi_2), '', paste0(coi_2, '.'))
    ) |> 
  arrange(desc(status))
```
\subsubsection{Concluded Research Support}
```{r grants_text}
#| results: asis
make_grants_table(grants, "concluded")
```

\subsection{Teaching and Lecturer Contributions} <!-- Improve the pull method from the cv database -->
\begin{longtable}{>{\raggedright\arraybackslash}p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Lecturer} & \textbf{Mar 2025 – Current} \\
\textsc{School of Medicine – Universidad Científica del Sur} & \textsc{Lima – Peru} \\
\textsc{Introduction to Epidemiology:} I teach three sections of \textasciitilde 15 fourth-year medical students each, focusing on basic clinical epidemiology concepts, including study designs, bias identification, \& basic epidemiological surveillance concepts. & \\
\newpage
\textbf{Teaching Assistant} & \textbf{Mar 2024 – Jun 2024} \\
\textsc{College of Arts \& Sciences – University of Washington} & \textsc{Seattle – USA} \\
\textsc{Introduction to Molecular and Cellular Biology:} Led two laboratory practice sessions with \textasciitilde 25 undergraduate students each, covering fundamental molecular and cellular biology experiments. & \\
\end{longtable}

\subsection{Advising}
```{r}
#| name: pooling_advising_data
advisees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' – ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', '\\textsc{', institution, '}',', ',country,' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
```
\subsubsection{Undergraduate Students}
```{r}
#| results: asis
advisees |> 
  filter(complete == 0) |>
  make_bullet_list_filtered("ug")
```

\section{Publications \hspace{1cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

```{r gstext, include = F, echo = F, eval = T}
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\subsection{Google Scholar Statistics:} `r text_gs`

```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0('\\uline{\\textbf{', journal_abbv, '}}')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = case_when(is.na(doi) ~ '',
                         doi == 'Submitted under consideration' ~ doi,
                         TRUE ~ paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')
       ),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) %>% 
  arrange(desc(year))
```

\subsection{Peer-Reviewed Publications}
```{r printing papers}
#| results: asis
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference Abstracts}
```{r printing abstracts, eval = T, include = T, echo = F}
#| results: asis
make_bullet_list_filtered(pubs, "conference")
```

\subsection{Thesis and Dissertations}
```{r printing theses, eval = T, include = T, echo = F}
#| results: asis
make_bullet_list_filtered(pubs, "thesis")
```

\subsection{White Papers}
```{r printing white papers, eval = T, include = T, echo = F}
#| results: asis
make_bullet_list_filtered(pubs, "white_paper")
```

\section{Licensure and Certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{>{\raggedright\arraybackslash}p{17cm} p{1cm}}
National Registry of Investigators \textsc{(RENACYT-CONCYTEC)}, Investigator Level VII (P0160977) & \textbf{2024} \\
CITI Program, Good Clinical Practice and ICH, Credential ID 65079238 & \textbf{2023} \\
CITI Program, Human Subjects Learners, Credential ID 65079240 & \textbf{2023} \\
CITI Program, Biomedical Responsible Conduct of Research, Credential ID 65079239 & \textbf{2023} \\
Peruvian Medical Board, License No. 94534 & \textbf{2021} \\
\end{longtable}

\section{Memberships in Professional Organizations}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{itemize}
 \item International Epidemiological Association (2020 - Current)
 \item Peruvian College of Physicians (2021 - Current)
 \item Consortium of Universities for Global Health (2023 - Current)
 \item America’s Network for Chronic Disease Surveillance (2025 - Current)
 \item Global Burden of Disease Study Collaborator (2025 – Current)

\end{itemize}